---
title: Cole (Nicholas) Mathis's Curriculum Vitae
graphics: yes
name: Cole
surname: Mathis
headcolor: 414141
#qualifications: 
position: "Assistant Professor"
address: "727 E Tyler St | Room 130C, Tempe, AZ 85281"
phone: "+1 480-459-8276"
www: colemathis.github.io
email: "cole.mathis@asu.edu"
twitter: colemathis__
github: colemathis
aboutme: |
  Computational \& Statistical Physicist. Origins of Life, Complex Systems, Life Detection, Molecular Assembly.
date: '`r format(Sys.Date(), "%B %d, %Y")`'
csl: "csl/apa7-cv-jy-edition.csl"
header-includes:
  # allow URLs to break at any character
  - \usepackage{xurl}
  # - \usepackage{fancyhdr}
  # - \pagestyle{fancy}
  # - \fancyhf{}
  # - \fancyhead[R]{\thepage}
knit: (function(input, ...) {lapply(bookdown::render_book(input, output_file = "docs/Cole_Mathis_CV", output_format = "all", envir = globalenv(), ...), browseURL)})
---

```{r setup, include=FALSE, cache = FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tidyverse)
library(vroom)
```

<!--chapter:end:index.Rmd-->

# Current Position

```{r Position}
library(tibble)
tribble(
    ~Position, ~Institution, ~Center, ~Title,
    "Assistant Professor", "Arizona State University", "Biodesign Institute", "Center for Biocomputation, Security, and Society",
    "Assistant Professor", "Arizona State University", "College of Global Futures", "School of Complex Adaptive Systems",
    "Founder & Treasurer", "Team 0", "", "39 Alpha Research",
    # "Visiting Assistant Professor", "Tokyo Tech", "World Research Hub", "Earth-Life Science Institute",
) %>%
    detailed_entries(Position, Institution, Title, Center)
```

<!--chapter:end:appointment.Rmd-->


# Experience

```{r Experience}
library(vitae)
library(lubridate)
vroom::vroom("data/experience.csv") %>%
    # select(-description) %>%
    # tidyr::fill(-description) %>%
    mutate(date = as.Date(start, "%m/%d/%Y")) %>%
    arrange(desc(date)) %>%
    detailed_entries( # Order of entries is a little weird here, but it looks good
        where = detail,
        when = glue::glue("{start} - {end}"),
        what = institution,
        with = position,
        why = description,
    )
```

<!--chapter:end:experience.Rmd-->

# Education

```{r}
library(tibble)
tribble(
    ~Degree, ~Year, ~Institution, ~Where,
    "PhD Physics", "2013-2018", "Arizona State University", "Tempe, Arizona",
    "BSc Physics", "2010-2013", "San Francisco State University", "San Francisco, California"
) %>%
    detailed_entries(Degree, Year, Institution, Where)
```

<!--chapter:end:education.Rmd-->

# Publications


**`#`**: Author of Correspondence.         **`*`**: Joint First authors.          **`-`**: Not Peer Reviewed.

<!-- # Selected Publications -->
<!--  -->
<!-- ::: {#refs_selected} -->
<!-- ::: -->


```{r Publications}
library(dplyr)
library(vitae)
library(tidyverse)
library(vroom)
bibliography_entries("data/pubs.bib") %>%
    arrange(desc(issued))
```


<!-- 
## Refereed Journal Papers

# ```{r}
# vitae::bibliography_entries("bib/journal.bib")
# # arrange(desc(row_number())) %>%
# # relocate(annote)
# ```

## Papers in Refereed Conference Proceedings
<!-- 
# ```{r}
# bibliography_entries("bib/proceedings.bib")
``` -->
<!--
## Book Chapters

# ```{r}
# bibliography_entries("bib/book.bib")
``` -->

<!--chapter:end:publication.Rmd-->

\pagebreak
# Invited Talks


```{r invited_talk}
vroom::vroom("data/talk.csv") %>%
    filter(invited == "Y") %>%
    dplyr::mutate(with = replace_na(with, " ")) %>%
    dplyr::mutate(when = lubridate::ym(when)) %>%
    dplyr::arrange(desc(when)) %>%
    dplyr::mutate(with = paste(with, " - ", why)) %>%
    vitae::detailed_entries(with, when, what, where, .protect = TRUE)
```
 
# Conferences, Workshops, and Seminars
```{r other_talk}
vroom::vroom("data/talk.csv") %>%
    dplyr::mutate(invited = replace_na(invited, " ")) %>%
    dplyr::mutate(why = replace_na(why, " ")) %>%
    filter(invited != "Y") %>%
    dplyr::mutate(with = replace_na(with, " ")) %>%
    dplyr::mutate(when = lubridate::ym(when)) %>%
    dplyr::arrange(desc(when)) %>%
    dplyr::mutate(with = if_else(why != " ", paste(with, " - ", why), with)) %>%
    vitae::detailed_entries(what, when, with, where, .protect = TRUE)
```

<!--chapter:end:presentation.Rmd-->


# Grants and Awards

```{r}
vroom::vroom("data/grant.csv") %>%
    tidyr::fill(-why) %>%
    vitae::detailed_entries(what, when, with, where)
```

<!--chapter:end:grant.Rmd-->

# Press and Media

```{r Press}
bibliography_entries("bib/media_coverage.bib") %>%
    arrange(desc(issued))
```

<!--chapter:end:media_coverage.Rmd-->

# Service & Outreach

## University Service

```{r service}
library(vitae)
vroom::vroom("data/committees-service.csv") %>%
  vitae::brief_entries(what, when, with, where)
```

## Mentorship
Test

## Founding Member, OoLEN (Origins of Life Early Career Network)

The Origin of Life Early career Network (OoLEN) supports and accelerates research on the Origin of Life by bringing together early-career scientists from very different disciplines and backgrounds. I founded this network together with Dr Joana Xavier, Dr Martina Preiner and Silke Asche. More information can be found at [oolen.org](https://oolen.org/).

## Conference Organizer
- Interdisciplinary Origin of Life Meeting for Early Career Researchers, University of Montreal, August 2022.
- New Frontiers in the Origins of Life, Santa Fe Institute, March 2022.
- Satellite Session, Conference on Complex Systems, Arizona State University, October 2015.

## Refereeing
- Astrobiology
- Life (MDPI)
- Nature Astronomy
- Scientific Reports
- Journal of the Royal Society: Interface Focus
- PloS Computational Biology,
- Journal of Molecular Evolution,
- Journal of the Royal Society: Phil Trans A 

<!--chapter:end:service.Rmd-->

# Summer & Winter Schools
```{r}
library(tibble)
library(vitae)
tribble(
    ~School, ~Year, ~Institution, ~Where,
    "Complex Systems Science Summer School", "2014", "Santa Fe Institute", "Santa Fe, New Mexico",
    "Josep Comas i Sola International Summer School in Astrobiology", "2015", "Universidad Internacional Menéndez Pelayo", "Santander, Spain"
) %>%
    detailed_entries(what = School, Year, Institution, Where)
```


# Field Experience

```{r}
tribble(
    ~Place, ~Year, ~Institution, ~Where, ~Why,
    "Yellowstone National Park", "2016", "GEOPIG, Arizona State University", "Montana, USA", "I worked closely with geologists, chemists, and microbiologists to collect samples and measurements from several hot spring environments in Yellowstone National park. I worked under the supervision of Prof Everett Shock"
) %>%
    detailed_entries( # Fucked up entries here again
        Institution,
        Year,
        Place,
        where = Where,
        why = Why
    )
```

<!--chapter:end:misc.Rmd-->

